\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2014-08-21 doc/sw-system.tex
Skeleton text about offline analysis, for #40

In this section we outline our methodology for interpreting the interactions
of the volunteers with the identification interface, and then describe how we
applied this methodology in the two classification stages in the CFHTLS
project.

@@

We perform an online analysis of the classifications,  updating a
probabilistic model of every (anonymous) volunteer's data, and also updating
the lens probability of each subject  (in both the training and test sets), on
a daily basis. This gives us a dynamic estimate of the posterior probability
for  any given  subject being a lens, given all classifications of it to date.
Assigning thresholds in this lens probability then allows us to make good
decisions about whether or not to retire a subject from the system, in order to
focus attention on new images.

@@

When all the subjects had either been retired, or classified around 10 times
or more, the web app was paused and reconfigured for stage 2. The sample of
subjects classified during stage 2 was selected to be all those that passed
the detection threshold ($\pr(\LENS|C,T) > 0.95$) at stage 1. These were
classified for one week, with no retirement but a maximum classification
number of 50 each.

\todo{Phil,Chris}{Write about offline analysis here (issue \#40)}

@@

How should we model these compressed data? The circumstances of each
classification are quite complex, as are the human classifiers in general: the
volunteers learn more about the problem as they go, but also inevitably make
occasional mistakes (perhaps because a lens is difficult to see, or they
became distracted during the task). To cope with this uncertainty, we assign a
simple software {\it agent} to partner each volunteer. The agent's task is to
interpret their volunteer's classification data as best it can, using a model
that makes a number of necessary approximations. These interpretations will
then include uncertainty arising as a result of the volunteer's efforts and
also the agent's approximations, but they will have two important redeeming
features. First, the interpretations will be quantitative (where before they
were qualititative),  and thus will be useful in decision-making. Second, the
agent will be able to predict, using its model, the probability of a test
subject being a $\LENS$, given both its volunteer's classification, and its
volunteer's experience. In this appendix we describe how these agents work.

@@

\subsection{Updating the Subject Probabilities}
\label{appendix:swap:examples}

@@

\todo{Phil,Chris}{Write about offline analysis here (issue \#40)}

>>>>

In this section we outline our methodology for interpreting the interactions
of the volunteers with the identification interface, and then describe how we
applied this methodology in the two classification stages in the CFHTLS
project in the \sw Analysis Pipeline (SWAP) code.\footnote{The open source 
SWAP code is available from 
\texttt{https://github.com/drphilmarshall/SpaceWarps}}

@@

While the \sw web app is live, and classifications are being made, we 
perform an online analysis of the classifications,  updating a
probabilistic model of every (anonymous) volunteer's data, and also updating
the lens probability of each subject  (in both the training and test sets), on
a daily basis. This gives us a dynamic estimate of the posterior probability
for  any given  subject being a lens, given all classifications of it to date.
Assigning thresholds in this lens probability then allows us to make good
decisions about whether or not to retire a subject from the system, in order to
focus attention on new images.

@@

When all the subjects had either been retired, or classified around 10 times
or more, the web app was paused and reconfigured for stage 2. The sample of
subjects classified during stage 2 was selected to be all those that passed
the detection threshold ($\pr(\LENS|C,T) > 0.95$) at stage 1. These were
classified for one week, with no retirement but a maximum classification
number of 50 each. {\bf The number of subjects at stage 2 was small enough that we
did not need to retire any: instead, we simply collected classifications for a
fixed period of time (about 4 weeks). Without the time pressure motivating the
online analysis, we implemented an ``offline'' version of the analysis that
performs a joint inference of all Agent confusion matrix elements and subject
probabilities simultaneously, for comparison. We describe how this differs
from the online analysis in the appendix. }

\todo{Chris}{Please check and edit the offline analysis description (in bold)
above -- and then the text in the appendix! (issue \#40)}

@@

How should we model these compressed data? The circumstances of each
classification are quite complex, as are the human classifiers in general: the
volunteers learn more about the problem as they go, but also inevitably make
occasional mistakes (perhaps because a lens is difficult to see, or they
became distracted during the task). To cope with this uncertainty, we assign a
simple software {\it agent} to partner each volunteer. The agent's task is to
interpret their volunteer's classification data as best it can, using a model
that makes a number of necessary approximations. These interpretations will
then include uncertainty arising as a result of the volunteer's efforts and
also the agent's approximations, but they will have two important redeeming
features. First, the interpretations will be quantitative (where before they
were qualititative),  and thus will be useful in decision-making. Second, the
agent will be able to predict, using its model, the probability of a test
subject being a $\LENS$, given both its volunteer's classification, and its
volunteer's experience. In this appendix we describe how these agents work,
and other aspects of the \sw analysis pipeline (SWAP).

@@

\subsection{Online SWAP: Updating the Subject Probabilities}
\label{appendix:swap:examples}

@@

\subsection{Offline SWAP}
\label{appendix:swap:offline}

The probabilistic model described above does not need to be implemented as an
online inference. Indeed, it might be more appropriate to perform the inference
of all Agent confusion matrix elements and Subject probabilities
simultaneously, so that the early classifications are not effectively
downweighted as a result of the Agent's ignorance. It might also be that this
ignorance builds in some conservatism to the system, reducing the noise due
the early classifications if they are unreliable. In the joint analysis, the
basic assumption that is built into the Agents, that their volunteers
have innate and unchanging talent for lens spotting parameterised by two 
constant confusion matrix elements which simply need to be inferred given the
data, is implemented in full. The effect is that of applying the time-averaged
confusion matrices, rather than one that evolves as the Agents (and in the
real world, the volunteers) learn.

The mathematics of the offline inference are presented elsewhere (in
preparation). Here we briefly note that we maximize the joint 
posterior probability distribution for all the model parameters (some 66,000
confusion matrix elements and 430,000 subject probabilities) with a simple
expectation-maximisation algorithm. This procedure takes [approximately the
same | somewhat less | somewhat more] CPU time as the online analysis, because
[insert reason]. Other comments about the relative performance]. The plots in
\Sref{sec:results:sample} show the difference in performance between the
online and offline analyses.

\todo{Chris}{Please check this text and edit appropriately (issue \#40)}
